MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-25 paper.Rmd
Better description of PFUSetup.

A second [targets][link-targets] pipeline 
in the [PFUAggDatabase][link-pfuaggdatabase] package [@Heun-PFUAggDatabase:2023]
aggregates ECCs
(a) by region 
(continents and world),
(b) by energy carrier (product) category 
(e.g., Coal and coal products, 
Low-, Medium-, and High-temperature heat, etc.), 
(c) by energy conversion machines (industries) and end use sectors
(e.g., Residential, Transport, etc.), and
(d) to primary, final, and useful (PFU) stages.
The [PFUAggDatabase][link-pfuaggdatabase]
pipeline uses the [Recca][link-recca] package extensively.
Both [targets][link-targets] pipelines 
(in the [PFUDatabase][link-pfudatabase] and
[PFUAggDatabase][link-pfuaggdatabase] packages)
benefit from the 
[PFUSetup][link-pfusetup] package, which
identifies a root directory and storage locations
for input and output data.

>>>>

A second [targets][link-targets] pipeline 
in the [PFUAggDatabase][link-pfuaggdatabase] package [@Heun-PFUAggDatabase:2023]
aggregates ECCs
(a) by region 
(continents and world),
(b) by energy carrier (product) category 
(e.g., Coal and coal products, 
Low-, Medium-, and High-temperature heat, etc.), 
(c) by energy conversion machines (industries) and end use sectors
(e.g., Residential, Transport, etc.), and
(d) to primary, final, and useful (PFU) stages.
The [PFUAggDatabase][link-pfuaggdatabase]
pipeline uses the [Recca][link-recca] package extensively.
Both [targets][link-targets] pipelines 
(in the [PFUDatabase][link-pfudatabase] and
[PFUAggDatabase][link-pfuaggdatabase] packages)
benefit from the 
[PFUSetup][link-pfusetup] package [@Heun-pfusetup:2023], which
identifies storage locations for input and output data.
